### 2020-04-16 survival.tex
reduced cox fig size
described failure and censoring

% !TEX root = main.tex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Survival Analysis
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Survival Analysis}
\label{section:survival}

@@

\begin{figure*}
  \includegraphics[width=6.5in]{figs/cox_o001.pdf}
  \caption{GPU hazard ratios from Cox regression model on {\tt old}
    batch.}
\end{figure*}
\begin{figure*}
  \includegraphics[width=6.5in]{figs/cox_n001.pdf}
  \caption{GPU hazard ratios from Cox regression model on {\tt new}
    batch.}
\end{figure*}

>>>>

% !TEX root = main.tex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Survival Analysis
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Survival Analysis}
\label{section:survival}
The construction of a GPU life time is more complex than it initially
appears because the units are observed only at reboot time and because
most units were proactively replaced to prevent failure.

We consider both OTB and DBE as failures for units that are removed
from the system and we record the inspection time as the failure
time. Most of the time, this is the last time such a unit is seen on
the system. In some cases, the last time seen is at a different time
but we still record its removal time as the failure time.

A key concept in survival analysis and in reliability is censoring,
which is about using information from study subjects whose exact
failure times are not available. This applies to our study because of
proactive GPU replacement before failure but also because of
observation only at inspection times (reboots). We use censoring
concepts on the proactive replacements. This allows us to use all of
the GPU life time data, including units that did not fail. But we
ignore the inspection time censoring, treating removal times as exact
failure times to reduce the complexity of this analysis. Because of
the weight of so much data, this would not make any difference in our
conclusions.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/cox_o001.pdf}
  \caption{GPU hazard ratios from Cox regression model on {\tt old}
    batch.}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/cox_n001.pdf}
  \caption{GPU hazard ratios from Cox regression model on {\tt new}
    batch.}
\end{figure}
